\textbf{How open are hybrid journals included in transformative agreements?}

### 2024-09-26 analysis/manuscript.Rmd
Submitted revision

The controversies surrounding hybrid open access and transformative agreements have led to varying policy conclusions. 
For instance, the British Joint Information Systems Committee (JISC) evaluated its open access strategy, which included transformative agreements [@Jisc_2024]. 
The evaluation revealed that while these agreements had a significant impact on the growth of open access in the country, they had limited effects in facilitating a global shift towards full open access. 
As a result, the report advised that the British open access strategy should be reassessed.
After making similar observation, Norwegian and Swedish universities and their consortia also argued for policy changes [@norway; @Widding_2024].
Furthermore, cOAlition S conclude its financial support of transformative agreements at the end of 2024, but continue to view open access resulting from such agreements as compliant. [^coalitions].
cOAlition S also removed the majority of hybrid journals from its Transformative Journal program in 2023 due to publishers' failure to meet self-defined open access growth targets [@Brainard_2023]. 
By contrast, the German DEAL consortium announced a five-year transformative agreement with Elsevier starting in 2024 and also renewed its contracts with Springer Nature and Wiley until the end of 2028. Similarly, the Colombia Consortium signed the first transformative agreements in Latin America [@Mu_oz_V_lez_2024].

>>>>

The controversies surrounding hybrid open access and transformative agreements have led to varying policy conclusions. 
For instance, the British Joint Information Systems Committee (JISC) evaluated its open access strategy, which included transformative agreements [@Jisc_2024]. 
The evaluation revealed that while these agreements had a significant impact on the growth of open access in the country, they had limited effects in facilitating a global shift towards full open access. 
As a result, the report advised that the British open access strategy should be reassessed.
After making similar observation, Norwegian and Swedish universities and their consortia also argued for policy changes [@norway; @Widding_2024].
Furthermore, cOAlition S conclude its financial support of transformative agreements at the end of 2024, but continue to view open access resulting from such agreements as compliant.[^coalitions]
cOAlition S also removed the majority of hybrid journals from its Transformative Journal program in 2023 due to publishers' failure to meet self-defined open access growth targets [@Brainard_2023]. 
By contrast, the German DEAL consortium announced a five-year transformative agreement with Elsevier starting in 2024 and also renewed its contracts with Springer Nature and Wiley until the end of 2028. Similarly, the Colombia Consortium signed the first transformative agreements in Latin America [@Mu_oz_V_lez_2024].

### 2024-09-26 analysis/manuscript.tex
Submitted revision

The controversies surrounding hybrid open access and transformative
agreements have led to varying policy conclusions. For instance, the
British Joint Information Systems Committee (JISC) evaluated its open
access strategy, which included transformative agreements (Brayman et
al., 2024). The evaluation revealed that while these agreements had a
significant impact on the growth of open access in the country, they had
limited effects in facilitating a global shift towards full open access.
As a result, the report advised that the British open access strategy
should be reassessed. After making similar observation, Norwegian and
Swedish universities and their consortia also argued for policy changes
(Holden et al., 2023; Widding, 2024). Furthermore, cOAlition S conclude
its financial support of transformative agreements at the end of 2024,
but continue to view open access resulting from such agreements as
compliant. \footnote{\url{https://www.coalition-s.org/coalition-s-confirms-the-end-of-its-financial-support-for-open-access-publishing-under-transformative-arrangements-after-2024/}}.
cOAlition S also removed the majority of hybrid journals from its
Transformative Journal program in 2023 due to publishers' failure to
meet self-defined open access growth targets (Brainard, 2023). By
contrast, the German DEAL consortium announced a five-year
transformative agreement with Elsevier starting in 2024 and also renewed
its contracts with Springer Nature and Wiley until the end of 2028.
Similarly, the Colombia Consortium signed the first transformative
agreements in Latin America (Muñoz-Vélez et al., 2024).

>>>>

The controversies surrounding hybrid open access and transformative
agreements have led to varying policy conclusions. For instance, the
British Joint Information Systems Committee (JISC) evaluated its open
access strategy, which included transformative agreements (Brayman et
al., 2024). The evaluation revealed that while these agreements had a
significant impact on the growth of open access in the country, they had
limited effects in facilitating a global shift towards full open access.
As a result, the report advised that the British open access strategy
should be reassessed. After making similar observation, Norwegian and
Swedish universities and their consortia also argued for policy changes
(Holden et al., 2023; Widding, 2024). Furthermore, cOAlition S conclude
its financial support of transformative agreements at the end of 2024,
but continue to view open access resulting from such agreements as
compliant.\footnote{\url{https://www.coalition-s.org/coalition-s-confirms-the-end-of-its-financial-support-for-open-access-publishing-under-transformative-arrangements-after-2024/}}
cOAlition S also removed the majority of hybrid journals from its
Transformative Journal program in 2023 due to publishers' failure to
meet self-defined open access growth targets (Brainard, 2023). By
contrast, the German DEAL consortium announced a five-year
transformative agreement with Elsevier starting in 2024 and also renewed
its contracts with Springer Nature and Wiley until the end of 2028.
Similarly, the Colombia Consortium signed the first transformative
agreements in Latin America (Muñoz-Vélez et al., 2024).
